Text embedding models reveal high resolution insights into conceptual knowledge from short multiple choice quizzes

### 2023-01-26 paper/main.tex
added andy as a co-author (yay!)
checking in a messy and incomplete version of the discussion section...

\author{Paxton C. Fitzpatrick and Jeremy R.
Manning\textsuperscript{*}\\Dartmouth
College\\\textsuperscript{*}Corresponding author:
jeremy.r.manning@dartmouth.edu}

@@

>>>>

\author{Paxton C. Fitzpatrick\textsuperscript{1},
Andrew C. Heusser\textsuperscript{1, 2}, and Jeremy R.
Manning\textsuperscript{1, *}\\\textsuperscript{1}Dartmouth
College\\\textsuperscript{2}Akili Interactive\\\textsuperscript{*}Corresponding author:
jeremy.r.manning@dartmouth.edu}

@@

\textbf{JRM NOTE: add overview of our findings.  Also need (lots of) citations below...}

Teaching, like effective writing and speaking, is fundamentally about empathy.
Great teachers consider students' interests, backgrounds, and working memory
capacities, and flexibly optimize their teaching strategies within those
constraints. In the classroom, empathizing with students also means maintaining
open lines of communication by fostering an environment in which all students
feel comfortable speaking up if they have an exciting new idea, or if they are
having trouble understanding something. In-person instruction also often
entails dynamic student-teacher and student-student interactions. These
in-person interactions can provide the instructor with valuable information
about students' understanding of the course material, beyond what they can
glean solely from exams or assignments. In turn, this can allow the instructor
to adapt their teaching approaches on-the-fly according to students' questions
and behaviors. But what does great teaching look like in asynchronous online
courses, when the instructor typically prepares course lectures and materials
without knowing who will ultimately be learning from them? Can the empathetic
side of teaching be automated and scaled?

The notion of empathy is tightly associated with ``theory of mind'' of other
individuals. Considering others' unique perspectives, prior experiences,
knowledge, goals, etc., can help us to more effectively interact and
communicate. The knowledge and learning maps we estimate in our study
(Fig.~\ref{fig:knowledge-maps}) hint at one potential form that an automated
empathetic teacher might take. We imagine that automated content delivery
systems that \textbf{JRM NOTE: CONTINUE....}

Over the past several years, the global pandemic has forced many educators to
teach remotely. This change in world circumstances is happening alongside (and
perhaps accelerating) geometric growth in the availability of high quality
online courses on platforms such as Khan Academy, Coursera, EdX, and others.
Continued expansion of the global internet backbone and improvements in
computing hardware have also facilitated improvements in video streaming,
enabling videos to be easily downloaded and shared by large segments of the
world's population. This exciting time for online course instruction provides
an opportunity to re-evaluate how we, as a global community, educate ourselves
and each other. For example, we can ask: what makes an effective course or
training program? Which aspects of teaching might be optimized or automated?
How and why do learning needs and goals vary across people? How might we lower
barriers to achieving a high quality education?

Alongside these questions, there is a growing desire to extend existing
theories beyond the domain of lab testing rooms and into real classrooms. In
part, this has led to a recent resurgence of ``naturalistic'' or
``observational'' experimental paradigms that attempt to better reflect more
ethologically valid phenomena that are more directly relevant to real-world
situations and behaviors. In turn, this has brought new challenges in data
analysis and interpretation. A key step towards solving these challenges will
be to build explicit models of real-world scenarios and how people behave in
them (e.g., models of how people learn conceptual content from real-world
courses, as in our current study). A second key step will be to understand
which sorts of signals derived from behaviors and/or other measurements (e.g.,
neurophysiological data; \textbf{CITE Hassan/Norman lab stuff, Poeppel lab
stuff, Para lab stuff, etc.}) might help to inform these models. A third major
step will be to develop and employ reliable ways of evaluating the complex
models and data that are a hallmark of naturalistic paradigms.

Ultimately, our work suggests a new line of questions regarding the future of
education: which aspects of teaching can be optimized and/or automated? The
social benefits of face-to-face instruction, such as social interactions,
friendships, and emotional support, cannot (and perhaps should not) be fully
replaced by an automated computer-based system. Nor can modern computer systems
experience emotional empathy in the human sense of the word. On the other hand,
perhaps it is possible to separate out the social aspects of classroom
instruction from the purely learning-related aspects. Our study shows that text
embedding models can uncover detailed insights into students' knowledge and how
it changes over time during learning.  We hope that these advances might help
pave the way for new ways of teaching or delivering educational content
that are tailored to individual students' learning needs and goals.
